---
title: "Data_Ninjas_dirty-data"
author: "Ethel Mensah"
date: "November 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dirty_data<-read.csv("C:/Users/mawufemor/Desktop/ANLY510-50 dirty_data/dirty_data.csv")
dirty_data
```
# Populate the missing values in the Area variable with an appropriate values (Birmingham, Coventry, Dudley, Sandwell, Solihull, Walsall or Wolverhampton) #

# Remove special characters, padding (the white space before and after the text) from Street 1 and Street 2 variables. Make sure the first letters of street names are capitalized and the street denominations are following the same standard (for example, all streets are indicated as "str.", avenues as "ave.", etc.#

# Removing special characters from street1 and street 2 columns in dirty data#
```{r}
dirty_data$Street<-gsub("[^a-zA-z\\.,]","", dirty_data$Street)
dirty_data$Street.2<gsub("[^a-zA-z\\.,]"," ", dirty_data$Street.2)
dirty_data
```
# Removing padding from street1 and street 2 columns in dirty data #

```{r}
dirty_data$Street<-trimws(dirty_data$Street, which = "both")
dirty_data$Street
dirty_data$Street.2<-trimws(dirty_data$Street.2, which = "both")
dirty_data
```

# Capitalizing the first letters of all the street names#
```{r}
dirty_data$Street<-tools::toTitleCase(tolower(dirty_data$Street))
dirty_data$Street.2<-tools::toTitleCase(tolower(dirty_data$Street.2))
dirty_data
```
